Contextual recruitment of selective attention can be updated via changes in task-relevance

### 2019-07-23 manuscript_pretty.Rmd
revision in-progress

Real-world environments can offer a plethora of context cues. For instance, consider someone writing in a coffee shop. The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop) associated with many experiences that afford different attentional priorities. Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching. Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention? On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues trigger attention in a ballistic manner [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977]. A writer's attention in this case would be at the mercy of the environment and the most strongly associated cues. On the other hand, contextual cuing of attention may not be entirely obligatory. Our current task-goals, for instance, might constrain the expression of previously learned associations, allowing, for instance, the laptop to take priority as a contextual cue over other cues that are irrelevant to the task at hand.

Historically, perspectives of automaticity and attentional control have emphasized the role of practice and likened the learning process to the development of automaticity in skill-learning [@schneider_controlled_1977; @shiffrin_controlled_1977; @logan_toward_1988; @logan_attention_1992]. Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities. Once formed however, they become habitual or hard-wired and the mere presence of the cue is suffificient to automatically adjust attention. Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977; @posner_attention_1975; @posner_facilitation_1975; @treisman_contextual_1960; @treisman_selective_1964; @treisman_strategies_1969]. This view is reflected in moodern work on contextual cuing where it is assumed that learned associations require practice [e.g., @lehle_fly_2008; @crump_learning_2016], form without awareness or intention, triggered automatically by the mere presence of the cue [@crump_context-specific_2006; @crump_contextual_2010; @crump_context-specific_2008; @king_priming_2012; @reuss_unconscious_2014; though, see @brosowsky_context-specific_2016].

>>>>

Real-world environments can offer a plethora of context cues. For instance, consider someone writing in a coffee shop. The coffee shop is a complex environment with numerous context cues (e.g., pictures on the wall, chairs, coffee, laptop), each of which we have different experiences with and afford different learned associations. Although a laptop might cue attentional processing helpful for writing, other features of the coffee shop might cue attentional processing related to other experiences like socializing and people-watching. Given that all of these cues are available to set attentional priorities, what determines which associative relationships will be used to guide attention? On the one hand, context-based retrieval of attentional priorities might be completely obligatory: the mere presence of learned cues might trigger attention in a ballistic manner [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977]. A writer's attention in this case would be at the mercy of the environment. On the other hand, contextual cuing of attention may not be entirely obligatory. Our current task-goals, for instance, might constrain the expression of previously learned associations, allowing, for instance, the laptop to take priority as a contextual cue over other cues that are irrelevant to the task at hand.

Historically, perspectives of automaticity and attentional control have emphasized the role of practice and likened the learning process to the development of automaticity in skill-learning [@schneider_controlled_1977; @shiffrin_controlled_1977; @logan_toward_1988; @logan_attention_1992]. Under this view, forming an association requires many repeated experiences pairing a cue with a set of attentional priorities. Once formed however, it becomes habitual or hard-wired and the mere presence of the cue is suffificient to automatically adjust attention. Learned associations are therefore ballistic, difficult to suppress, and difficult to unlearn [e.g., @schneider_controlled_1977; @shiffrin_controlled_1977; @posner_attention_1975; @posner_facilitation_1975; @treisman_contextual_1960; @treisman_selective_1964; @treisman_strategies_1969]. This view is reflected in modern work on contextual cuing where it is assumed that learned associations require practice [e.g., @lehle_fly_2008; @crump_learning_2016], form without awareness or intention, and are triggered automatically by the mere presence of the cue [@crump_context-specific_2006; @crump_contextual_2010; @crump_context-specific_2008; @king_priming_2012; @reuss_unconscious_2014; though, see @brosowsky_context-specific_2016].
